A performance assessment of evolutionary algorithms in volunteer computing environments

### 2016-11-07 EvoPar2017/paper.Rnw
Anonymizes this

\author{Juan-J.~Merelo \and Paloma de las Cuevas \and Pablo
  Garc\'ia-S\'anchez \inst{1} \and Mario Garc\'ia-Valdez \inst{2}}

\institute{Dept. of Computer Architecture and Technology, University
of Granada, Spain \and
Dept. of Graduate Studies at Instituto Tecnol\'ogico de Tijuana}

@@

%This work has been supported in part by TIN2014-56494-C4-3-P (Spanish
%Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio
%2015 UGR). We are also grateful to {\tt @otisdriftwood} for his help
%gathering users for the new experiments.

>>>>

%% \author{Juan-J.~Merelo \and Paloma de las Cuevas \and Pablo
%%   Garc\'ia-S\'anchez \inst{1} \and Mario Garc\'ia-Valdez \inst{2}}
\author{First Author \and Second Author}

%% \institute{Dept. of Computer Architecture and Technology, University
%% of Granada, Spain \and
%% Dept. of Graduate Studies at Instituto Tecnol\'ogico de Tijuana}
\institute{First Institute in Somecountry \and Second University in Someothercountry}

@@

%This work has been supported in part by TIN2014-56494-C4-3-P (Spanish
%Ministry of Economy and Competitivity), PROY-PP2015-06 (Plan Propio
%2015 UGR). We are also grateful to {\tt @otisdriftwood} for his help
%gathering users for the new experiments.
Acknowledgements\\
taking\\
this\\
space
